CMPSubset

### 2021-08-16 CMP/CMPSubset.Rmd
Generate Biomark candidates for 85% var (dim18), res1 and res1.5

```{r}
source("../RFunctions/read_10XGenomics_data.R")
source("../RFunctions/PercentVariance.R")
source("../RFunctions/Mouse2Human_idconversion.R")
```

@@

## Identify variable genes for new biomark
```{r}
length(cmp.object@assays$RNA@var.features)
```
```{r}
top100.var <- cmp.object@assays$RNA@var.features[1:100]
length(top100.var)
```

@@

saveRDS(cmp.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
```
Plot UMAP

@@

saveRDS(cmp.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
```
Plot UMAP

>>>>

```{r}
source("../RFunctions/read_10XGenomics_data.R")
source("../RFunctions/PercentVariance.R")
source("../RFunctions/Mouse2Human_idconversion.R")
source ("../RFunctions/ColorPalette.R")
```

@@

@@

```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	cmp.object <- FindClusters(cmp.object, resolution = x)
saveRDS(cmp.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
}
```

## Identify variable genes for new biomark
```{r}
length(cmp.object@assays$RNA@var.features)
```

### Gene profiles of clusters
set ident at res = 1 and get markers
```{r}
Idents(cmp.object) <- "RNA_snn_res.1"
cmp.allmarkers.res1 <- FindAllMarkers(cmp.object)
cmp.top100markers.res1 <- cmp.allmarkers.res1 %>% group_by(cluster) %>% top_n(n = 100, wt = abs(avg_log2FC))
```

```{r}
cmp.top100markers.res1 <- cmp.allmarkers.res1 %>% group_by(cluster) %>% top_n(n = 100, wt = abs(avg_log2FC))
cmp.top100markers.res1 <- cmp.top100markers.res1[cmp.top100markers.res1$p_val_adj <= 0.05, ]
for(cluster in unique(cmp.top100markers.res1$cluster)){
	num.hits <- nrow(cmp.top100markers.res1[cmp.top100markers.res1$cluster == cluster, ])
	print(paste("cluster", cluster, "has", num.hits, "genes"))
}
```

Find top.var	genes in cmp.top100markers.res1
```{r}
top.var <- cmp.object@assays$RNA@var.features[1:150]
# top.var
n.vargenes <- c()
for(gene in top.var){
	if(gene %in% cmp.top100markers.res1$gene){
		n.vargenes <- c(n.vargenes, gene)
	}
}
print(length(n.vargenes))
top.var[!(top.var %in% n.vargenes)]
```

Lets try to export these, with genes on rows and clusters on columns, and xpression value in data table
```{r}
var.df <- cmp.top100markers.res1[cmp.top100markers.res1$gene %in% n.vargenes,]
var.df <- subset.data.frame(var.df, select = c("gene", "cluster", "avg_log2FC"))
var.df <- reshape2::dcast(var.df, gene~cluster, value.var = "avg_log2FC")
xlsx::write.xlsx(var.df, file = paste0(projectName, "_dim", ndims, "_candididateBiomarkGenes.xlsx"), sheetName = "res1", append = TRUE, row.names = FALSE)

repeat for top.var	genes in cmp.top100markers.res1.5
```{r}
top.var <- cmp.object@assays$RNA@var.features[1:150]
Idents(cmp.object) <- "RNA_snn_res.1.5"
cmp.allmarkers.res1.5 <- FindAllMarkers(cmp.object)
cmp.top100markers.res1.5 <- cmp.allmarkers.res1.5 %>% group_by(cluster) %>% top_n(n = 100, wt = abs(avg_log2FC))
n.vargenes <- c()
for(gene in top.var){
	if(gene %in% cmp.top100markers.res1.5$gene){
		n.vargenes <- c(n.vargenes, gene)
	}
}
print(length(n.vargenes))
top.var[!(top.var %in% n.vargenes)]
```

Lets try to export these, with genes on rows and clusters on columns, and xpression value in data table
```{r}
var.df <- cmp.top100markers.res1.5[cmp.top100markers.res1.5$gene %in% n.vargenes,]
var.df <- subset.data.frame(var.df, select = c("gene", "cluster", "avg_log2FC"))
var.df <- reshape2::dcast(var.df, gene~cluster)
xlsx::write.xlsx(var.df, file = paste0(projectName, "_dim", ndims, "_candididateBiomarkGenes.xlsx"), sheetName = "res1.5", append = TRUE, row.names = FALSE)

```
For each resolution, what percentage of cells in each cluster are enriched for one of our clust.IDs?

# Total var 80%
## Neighborhood and umap
set total.var <- 80%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 80))

```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	cmp.object <- FindClusters(cmp.object, resolution = x)
saveRDS(cmp.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
}
```

@@
